---
title: "c_mulvey_r_solo"
output: html_notebook
---

```{r}
library(tidyverse)
```


1.Read in districts.csv into a tibble named districts. How many rows and columns does it contain?

```{r}
districts <- read_csv('../data/districts.csv')
```
There are 146 rows and 27 columns.

2.Notice that the first row corresponds to the whole State of Tennessee. Remove this row and save the result back to districts.

```{r}
districts <- districts[-1,]
```

3. How many districts have a proficiency rate of at least 80% for both alg_1 and eng_1?

```{r}
districts %>% 
  filter(alg_1 > 80 & eng_1 > 80) %>% 
  count()
```

4. How many districts have a proviciency rate less than 50% for either alg_1 or eng_1?

```{r}
districts %>% 
  filter(alg_1 < 50 | eng_1 < 50) %>% 
  count()
```

5. Which district has the lowest graduation rate?

```{r}
districts %>% 
  filter(grad == min(grad, na.rm = TRUE))
```

6. Which district has the highest dropout rate?

```{r}
districts %>% 
  filter(dropout == max(dropout, na.rm = TRUE))
```

7. Within the Mid Cumberland region, which district has the highest ACT composite?

```{r}
districts %>% 
  filter(region == 'Mid Cumberland') %>% 
  filter(act_composite == max(act_composite, na.rm = TRUE))
```

8. Create a histogram showing the distribution of graduation rates. What can you say about this distribution?

```{r}
districts %>% 
  ggplot(aes(x = grad)) +
  geom_histogram()
```
The distribution is left skewed.


9. Create a scatter plot to compare alg_1 proficiency rates to alg_2 rates. What do you notice? Facet this plot by region. Does anything stand out when you facet the plots?

```{r}
districts %>% 
  ggplot(aes(x = alg_1, y = alg_2)) +
  geom_point() +
  facet_wrap(~ region)
```

10. Create a bar chart showing the total enrollment by region. Which region has the highest total enrollment? Which has the smallest?

```{r}
districts %>% 
  group_by(region) %>%
  mutate(region_enrollment = sum(enrollment, na.rm = TRUE)) %>% 
  ggplot(aes(x = region, y = region_enrollment)) +
  geom_col()
```
Mid Cumberland has the highest enrollment and Northwest has the smallest.


11.When creating this bar chart you may have noticed that some districts have missing enrollment values. For how many districts is this the case?

```{r}
districts %>% 
  filter(is.na(enrollment)) %>% 
  count()
```

12. What is the mean graduation rate across all districts? What might be wrong with using just the regular mean to assess average graduation rates?

```{r}
districts %>% 
  summarize(mean(grad, na.rm = TRUE))
```


# 13. Redo the previous question but use a weighted average (weighted.mean) graduation across all districts, weighing by enrollment. How much does this change your answer? Can you explain using the data the reason for the big change from using the mean?

```{r}
districts %>% 
  summarize(weighted.mean(grad, enrollment, na.rm = TRUE))
```

14. Create a boxplot showing enrollment rates per region. Does anything stand out?

```{r}
districts %>% 
  group_by(region) %>% 
  ggplot(aes(x = ed)) +
  geom_boxplot()
```

15. Create a boxplot showing graduation rates per region. Does anything stand out?

```{r}
districts %>% 
  group_by(region) %>% 
  ggplot(aes(x = grad)) +
  geom_boxplot()
```























